A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-28 UAM2014/Article/article.tex
la2pdf commit - 2014:04:28	01:35:48	(Mon28.Apr)
la2pdf commit - 2014:04:28	11:03:27	(Mon28.Apr)

\newlength\oldparindent
\setlength\oldparindent{\parindent}

@@

\title{A GPU Sonar Simulator for Automatic Target Recognition}%
%
\author{J.I.Buskenes\firstAddress, C.-I.C.Nilsen\secondAddress, A.Austeng\secondAddress}%
%
\begin{contact}
  \firstAddress Dept. of Informatics, P.O.Box 1080 Blindern, N-0316 OSLO
  \secondAddress Norwegian Defence Research Establishment (FFI) P.O.Box 25, NO-2027 Kjeller
\end{contact}%
%
\begin{contact}
Contact author: Jo Inge Buskenes\\
Dept. of Informatics, Univ. of Oslo, P.Box 1080 Blindern, N-0316 OSLO\\
\href{mailto:joibu@ifi.uio.no}{joibu@ifi.uio.no}
\end{contact}%
%
\begin{abstract}
Template matching is a common technique used when classifying objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing an object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a suitable set of template images considering that no seabed or object is truly alike.

@@

A synthetic aperture sonar (SAS) utilizes a wider along-track beam to ensonify the same part of the seafloor with several sucessive pings. Later this data is combined coherently to allow the synthetization of a much larger receiving array, which drastically improves the along-track resolution.

@@

OpenGL is a framework that

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{Simulated cylinder.}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_bw.svg}%
\caption{Simulated cylinder.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Simulated cylinder (adaptive).}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive_bw.svg}%
\caption{Simulated cylinder (adaptive).}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

@@

>>>>

\definecolor{tabBlue}{HTML}{AACCFF}
\newlength\oldparindent
\setlength\oldparindent{\parindent}

@@

\title{A GPU Sonar Simulator for Automatic Target Recognition}%
%
\author{J.I.Buskenes\firstAddress, \O{}ivind Midtgaard\secondAddress, Herman Midelfart\secondAddress}%
%
\begin{contact}
  \firstAddress Dept. of Informatics, P.O.Box 1080 Blindern, N-0316 OSLO
  \secondAddress Norwegian Defence Research Establishment (FFI) P.O.Box 25, NO-2027 Kjeller
\end{contact}%
%
\begin{contact}
Contact author: Jo Inge Buskenes\\
Dept. of Informatics, Univ. of Oslo, P.Box 1080 Blindern, N-0316 OSLO\\
\href{mailto:joibu@ifi.uio.no}{joibu@ifi.uio.no}
\end{contact}%
%
\begin{abstract}
Template matching is a common technique used when classifying objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing an object of interest, correlate it with a set of template images, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a suitable set of template images considering that no seabed or object is truly alike.

@@

% A synthetic aperture sonar (SAS) utilizes a wider along-track beam to ensonify the same part of the seafloor with several sucessive pings. Later this data is combined coherently to allow the synthetization of a much larger receiving array, which drastically improves the along-track resolution.

@@

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{Cylinder simulation with ``typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$. }\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_bw.svg}%
\caption{Cylinder simulation with ``typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Adaptive cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive_bw.svg}%
\caption{Adaptive cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

@@

\begin{table}[bh]
TODO: Probably not necessary to have this table...\\
\begin{tabular}[c]{l l l l l}\hline
\rowcolor{tabBlue} & cor   & ecor  & scor  & essum \\\hline
Standard template & 0.461 & 0.698 & 0.528 & 0.613 \\
Adaptive template & 0.673 & 0.818 & 0.807 & 0.813
\end{tabular}
\caption{Correlation scores. Description:\newline
cor - correlation between image and template calculated over all pixels in the image\newline
ecor - correlation calculated over the union of the echo pixels in the image\newline
scor - correlation calculated over the union of the echo pixels in image and template\newline
essum - 0.5*(ecor+scor). Average of the echo and shadows}
\end{table}

Reference correlation scores~\cite{Midelfart2010}
